Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions

### 2022-05-12 Article.tex
Add Appendix A and details about ANN

\usepackage{multirow}
%\usepackage{rotating} %Pour effectuer la rotation d'un tableau à  l'aide de "\begin{sidewaystable} et \end{}" et supprimer "\begin{table} et \end{}"
\usepackage{pdflscape}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

%\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\e}[1]{\mbox{\ensuremath{\mathrm{e}^{#1}}}}
\DeclareMathOperator{\sigmoid}{sig}

@@

In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter. The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, T) and one output (the yield stress, $\sigma^y$). The global architecture of this kind of ANN is given in Figure \ref{ANN}.

@@

A Sigmoid activation function defined by equation (\ref{eq:sigmoid}) is used for all neurons in the two hidden layers, but none is used for the output neuron.
\begin{equation}
\sigmoid(x)=\frac{1}{1 + \e{-x}}\label{eq:sigmoid}
\end{equation}
Because of the large number of identified parameters for the whole ANN model (from 122 to 210 for 9 and 17 neurons for the first hidden layer, respectively); the 5 sets of ANN parameters used in this publication are provided in \cite{pantale_coefficients_2022}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The Appendices part is started with the command \appendix;
%%% appendix sections are then done as normal sections
%%% \appendix
%
%%% \section{}
%%% \label{}
%
%%% References
%%%
%%% Following citation commands can be used in the body text:
%%% Usage of \cite is as follows:
%%%   \cite{key}          ==>>  [#]
%%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%%   \citet{key}         ==>>  Author [#]
%
%%% References with bibTeX database:
%
\bibliographystyle{model1-num-names}
\bibliography{Biblio}
%
%%% Authors are advised to submit their bibtex database files. They are
%%% requested to list a bibtex style file in the manuscript if they do
%%% not want to use model1-num-names.bst.
%
%%% References without bibTeX database:
%
%% \begin{thebibliography}{00}
%

>>>>

\usepackage{multirow}
%\usepackage{rotating} %Pour effectuer la rotation d'un tableau à  l'aide de "\begin{sidewaystable} et \end{}" et supprimer "\begin{table} et \end{}"
\usepackage{pdflscape}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{pgfplots}
\usepackage{accents}

%\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\e}[1]{\mbox{\ensuremath{\mathrm{e}^{#1}}}}
\DeclareMathOperator{\sigmoid}{sig}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\dotp}{\boldsymbol{\cdot}}
\newcommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}

@@

In order to verify the influence of the complexity of the neural network on the numerical results of the simulation and the computing time, several architectures of ANN are tested thereafter. The chosen global architecture has 2 hidden layers with a variable number of neurons for the first hidden layer ($\zeta$ = 9 to 17) and 7 neurons for the second hidden layer, 3 inputs (plastic strain, $\varepsilon^p$, plastic strain rate, ${\dot{\varepsilon}}^p$, and temperature, $T$) and one output (the yield stress, $\sigma^y$). The global architecture of this kind of ANN is given in Figure \ref{ANN} for 9 neurons in the first hidden layer. Conforming to Pantalé et al. \cite{pantale_efficient_2022}, this ANN is referred after the terminology ANN 3-9-7-1-sig, because it has 3 inputs, 9 neurons in the first hidden layer, 7 neurons in the second hidden layer, 1 output and a sigmoid activation function.

@@

The main advantage of this approach (the use of an ANN), after the training phase, is that the output $\sigma^y$ of the network is related to the inputs $\varepsilon^p$, ${\dot{\varepsilon}}^p$, and $T$ through equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}). The first step is to scale the input data to the interval $[0,1]$ using the following equation:

\begin{equation}
\overrightarrow{x} =
\begin{cases}
x_1 = \frac{\varepsilon^p - [\varepsilon^p]_{min}}{[\varepsilon^p]_{max} - [\varepsilon^p]_{min}}\\
x_2 = \frac{\ln(\mdot{\varepsilon}^p)-[\ln(\mdot{\varepsilon}^p)]_{min}}{[\ln(\mdot{\varepsilon}^p)]_{max}-[\ln(\mdot{\varepsilon}^p)]_{min}}\label{eq:ANN-preprocess}\\
x_3 = \frac{T-[T]_{min}}{[T]_{max}-[T]_{min}}
\end{cases}
\end{equation}

The output of the neurons in the first hidden layer are given by the following equation:

\begin{equation}
\overrightarrow{y_1} = \sigmoid\left(\w_1 \dotp \overrightarrow{x}+ \overrightarrow{b_1}\right)\label{eq:ANN-y1}
\end{equation}
where, a $\sigmoid()$ is the sigmoid activation function defined by equation (\ref{eq:sigmoid}).
\begin{equation}
\sigmoid(x)=\frac{1}{1 + \e{-x}}\label{eq:sigmoid}
\end{equation}

Then, the output of the neurons in the second hidden layer are given by equation (\ref{eq:ANN-y2}).
\begin{equation}
\overrightarrow{y_2} = \sigmoid\left(\w_2 \dotp \overrightarrow{y_1}+ \overrightarrow{b_2}\right)\label{eq:ANN-y2}
\end{equation}

So, that, the output of the ANN is therefore given by equation (\ref{eq:ANN-vonMises}).
\begin{equation}
\sigma =  \left([\sigma]_{max}-[\sigma]_{min}\right) \left(\overrightarrow{w}^T \dotp \overrightarrow{y_2} + b\right) + [\sigma]_{min} \label{eq:ANN-vonMises}
\end{equation}

In equations (\ref{eq:ANN-preprocess}) to (\ref{eq:ANN-vonMises}), quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$ are given by the training procedure of the ANN. Corresponding values for an ANN containing 9 neurons in the first hidden layer are reported in \ref{sec:appendix-1}. Quantities $[\ ]_{min}$ and $[\ ]_{max}$  are the boundaries of the range of the corresponding field during the training phase, values are also given in \ref{sec:appendix-1}.

Because of the large number of identified parameters for all the ANN models (from 114 to 202 for 9 and 17 neurons for the first hidden layer, respectively); the other 4 sets of ANN parameters used in this publication can be found in \cite{pantale_coefficients_2022}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The Appendices part is started with the command \appendix;
%%% appendix sections are then done as normal sections
\appendix
%
\section{Coefficients of the ANN 3-9-7-1-sig\label{sec:appendix-1}}

In this Appendix, we present the values obtained after the training phase of an ANN containing 9 neurons in the first hidden layer and 7 neurons in the second hidden layer.

The training of the neural network was performed using a data set containing $3\,430$ data points defined by:
\begin{itemize}
\item $70$ values for $\varepsilon^p\in[0.0,3.0]$, so that $[\varepsilon^p]_{min}=0$ and $[\varepsilon^p]_{max}=3$.
\item $7$ plastic strain rates $\mdot{\varepsilon}^p\in[1, 10, 50, 500, 5\,000, 50\,000, 500\,000]$, so that $[\ln(\mdot{\varepsilon}^p)]_{min}=0$ and $[\ln(\mdot{\varepsilon}^p)]_{max}=13.12236$.
\item  $7$ temperatures $T\in[293, 400, 500, 700, 900, 1\,200, 1\,500]$, so that $[T]_{min}=293$ and $[T]_{max}=1\ 500$.
\end{itemize}

Stresses in the training dataset ranges from $[\sigma]_{min}=171.44$ to $[\sigma]_{max}=2606.12$.
The results of the training process are given below for quantities $\w_1$, $\w_2$, $\overrightarrow{w}$, $\overrightarrow{b_1}$, $\overrightarrow{b_2}$ and $b$.

\begin{equation*}
\w_1=\left[
\begin{array}{rrr}
 -0.87229 & -0.47675 & -1.50771\\
 -0.95762 & -0.25619 &  1.65222\\
 -10.61660 &  0.22003 & -0.11539\\
  3.67883 &  0.37146 & -1.51069\\
 -63.39468 &  0.15466 & -0.95431\\
  0.54807 &  0.25959 & -5.44355\\
 -1.33883 &  0.36089 & -1.66735\\
 -0.68125 &  1.02121 &  0.34242\\
  0.08740 &  0.18764 & -41.32542
\end{array}\right]
\end{equation*}

\begin{equation*}
\w_2^T=\left[
\begin{array}{rrrrrrrrr}
  1.66285 & -0.59645 & -3.17333 &  0.20706 &  1.18760 &  2.01250 & -0.82147\\
 -0.26237 & -2.50330 & -1.45941 & -1.59833 &  4.05169 & -1.21146 &  1.05610\\
 -0.12958 &  0.67119 & -5.85989 & -2.55061 &  4.85245 &  4.31876 &  3.24070\\
 -2.12890 &  0.68296 &  0.71183 &  0.81706 & -0.09405 &  0.34919 & -1.41223\\
  2.33631 & -0.08089 &  14.65789 &  0.12531 &  23.66363 &  2.55872 &  2.15338\\
  0.11567 &  1.77629 & -1.80448 &  0.77825 & -1.58254 &  1.90442 &  1.23152\\
  1.49265 &  0.41821 & -3.53803 & -0.48705 & -0.23671 &  0.75887 & -0.37441\\
  0.95990 &  0.69041 &  0.43870 &  0.28393 & -1.40101 & -0.64569 & -0.38964\\
  5.89937 & -0.13015 &  2.99264 &  1.78534 & -3.90189 &  1.17494 & -3.78854
\end{array}\right]
\end{equation*}

\begin{equation*}
\overrightarrow{w}=\left[
\begin{array}{r}
  0.34701\\
  1.42079\\
 -0.96564\\
  0.62467\\
 -0.56322\\
  0.40960\\
 -0.42810
\end{array}\right]
\end{equation*}

\begin{equation*}
\overrightarrow{b_1}=\left[
\begin{array}{r}
  2.57141\\
  0.22673\\
 -1.16985\\
 -0.11246\\
 -0.82210\\
 -2.13264\\
  0.78794\\
  1.20434\\
 -3.48681
\end{array}\right]
\end{equation*}

\begin{equation*}
\overrightarrow{b_2}=\left[
\begin{array}{r}
 -0.36566\\
 -1.14445\\
 -0.79065\\
 -0.50670\\
  1.30136\\
  0.04521\\
 -0.29995
\end{array}\right]
\end{equation*}

\begin{equation*}
b=0.04213
\end{equation*}

%%% \section{}
%%% \label{}
%
%%% References
%%%
%%% Following citation commands can be used in the body text:
%%% Usage of \cite is as follows:
%%%   \cite{key}          ==>>  [#]
%%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%%   \citet{key}         ==>>  Author [#]
%
%%% References with bibTeX database:
%
\bibliographystyle{model1-num-names}
\bibliography{Biblio}
%
%%% Authors are advised to submit their bibtex database files. They are
%%% requested to list a bibtex style file in the manuscript if they do
%%% not want to use model1-num-names.bst.
%
%%% References without bibTeX database:
%
%% \begin{thebibliography}{00}
%
